Statistical stopping criteria for automated screening in systematic reviews

### 2023-03-14 pres/stopping_2023.tex
biased pres

\title[Stopping Criteria]{Statistical stopping criteria for automated screening in systematic reviews}
\date{20 October 2022}
\author{Finn Müller-Hansen, Max Callaghan}
\institute[MCC]{
	\includegraphics[height=1cm,width=2cm]{images/MCC_Logo_RZ_rgb.jpg}
}

@@

@@

	Twitter: \url{https://twitter.com/MaxCallaghan5}

>>>>

\title[Stopping Criteria]{Statistical stopping criteria for automated screening in systematic reviews}
\date{20 October 2022}
\author{Max Callaghan, Finn Müller-Hansen}
\institute[MCC]{
	\includegraphics[height=1cm,width=2cm]{images/MCC_Logo_RZ_rgb.jpg}
}

@@

\begin{frame}{Biased urns}

		\column{0.382\textwidth}
		\only<1->{
			\begin{figure}
				\includegraphics[width=\linewidth]{../../biased-rapid-review/plots/bias.pdf}
			\end{figure}
		}

		\column{0.6\textwidth}

		\begin{itemize}
			\item<1-> Our original criteria treats documents as if they were drawn at random from an urn
			\item<2-> In fact, they are drawn in descending order of their predicted relevance
			\item<3-> Using a non-central hypergeometric distribution \citep{fog_calculation_2008}, we can input a \textbf{bias} parameter indicating how much more likely we are to draw a random relevant than a random non-relevant document.
			\item<4-> Estimating this parameter is empirically non-trivial!
		\end{itemize}

\begin{frame}{Realistic empirical evaluations for AI}

\begin{remark}
	To know when it is safe to use AI systems in future evidence synthesis projects, we need to evaluate them on past data \textbf{under realistic conditions}
\end{remark}

In living evidence applications:

\begin{itemize}
	\item<2-> How long can we trust classifier evaluations without labelling new data?
	\item<3-> How does topic model fit decay over time?
	\item<4-> How do we incorporate new topics?
	\item<4-> How frequently \textit{would} LRs have been updated? Is this predictable?
\end{itemize}

@@
